%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper, 10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ulem}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{4pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\altSubheading}[3]{
  \vspace{4pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}, {#2} & #3 \\
    \end{tabular*}\vspace{-8pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{4pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-8pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\huge \scshape Ben Xia} \uline{} \\ \vspace{1pt}
  \small (858)-357-1594 $|$
  \href{mailto:benjx32@gmail.com}{\uline{benjx32@gmail.com}} $|$
  \href{mailto:bbxia@ucsd.edu}{\uline{bbxia@ucsd.edu}} $|$
  \href{https://linkedin.com/in/benjxia}{\uline{linkedin.com/in/benjxia}} $|$
  \href{https://github.com/benjxia}{\uline{github.com/benjxia}}
\end{center}
\vspace{-16pt}



%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
      {University of California San Diego}{Sept. 2024 -- June 2025}
      {Master of Science in Computer Science}{[GPA: 4.00/4.00]}
  \resumeSubheading
      {University of California San Diego}{Sept. 2021 -- June 2024}
      {Bachelor of Science in Computer Science}{Honors: Summa Cum Laude [GPA: 3.98/4.00]}
  \resumeSubHeadingListEnd
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Courses}{: AI/Machine Learning, Deep Learning, Advanced Computer Vision, Natural Language Processing, Computer Graphics, Parallel Computing, Operating Systems, Computer Security, Data Structures, Algorithms, Computer Architecture, Virtualization/Cloud Computing} \\
    }}
 \end{itemize}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \vspace{4pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C, C++, Python, CUDA, OpenCL, Java, C\#, Go, x86/ARM Assembly, SQL, HTML, CSS, JavaScript/TypeScript } \\
     \textbf{Libraries/Frameworks}{: PyTorch, React, Node.js, NumPy,  OpenCV, scikit-learn, OpenGL, Message Passing Interface (MPI) } \\
     \textbf{Developer Tools}{: Git, Docker, Perforce, Jira, Confluence, GitHub Actions, Jenkins, Vim} \\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \altSubheading
    {Amazon}{Software Development Engineer Intern}{Sept. 2024 -- Dec. 2024}
    \resumeItemListStart
      \resumeItem{ Leveraged \textbf{AWS Bedrock Large Language Models} to design/deliver a new notification summarization feature to reduce user fatigue. }
      \resumeItem{ Integrated safeguards for \textbf{customer-facing LLM endpoints} by enforcing \textbf{cryptographic signatures} against request forgery, \textbf{rate-limiting} requests, and Bedrock guardrails against adversarial user inputs. }
      \resumeItem{ Built support for iOS time-sensitive notifications for an app with \textbf{200 million+} users and \textbf{10000+} transactions per second, enabling critical alerts to bypass Do Not Disturb settings with \textbf{AWS SNS}, Java and \textbf{Swift}. }
      \resumeItem{ \textbf{Eliminated} manual developer intervention by building a self-service system with \textbf{React, Redux}, \textbf{AWS DynamoDB} and \textbf{ECS}, enabling marketing teams and automatic services to directly attach images to push notifications. }
      \resumeItemListEnd
    \altSubheading
    {Niantic}{Computer Vision Engineer Intern}{June 2024 -- Sept. 2024}
    \resumeItemListStart
      \resumeItem{ Partnered with UX designers to develop an intuitive \textbf{augmented reality} 3D space scanning preview by writing custom GLSL shaders and points of interest detectors, allowing users to easily identify under-reconstructed areas in real-time during scans. }
      \resumeItem{ Implemented \textbf{real-time occlusion} support in Niantic 8th Wall's internal AR engine, elevating immersion in AR experiences. }
      \resumeItem{ Boosted \textbf{Gaussian splat} reconstruction quality by multithreading training/rendering routines and switching to raster-based splat rendering with C++ and OpenGL, \textbf{increasing frames processed by 100\%}, while simultaneously improving overall performance. }
      \resumeItem{ Increased live preview performance by \textbf{200+\%} (frames per second) on Android devices, significantly enhancing app responsiveness and user experience by reducing micro-stutters and \textbf{optimizing OpenCL GPU kernels}. }
      \resumeItemListEnd
    \altSubheading
    {Viasat}{Software Engineer Intern}{June 2023 -- Sept. 2023}
    \resumeItemListStart
      \resumeItem{Resolved race conditions for \textbf{real-time embedded systems} in C, preventing over \textbf{\$5000} in potential aircraft antenna unit damages by redesigning state machines and restricting IPC messages between \textbf{operating system daemons} based on log analysis.}
      \resumeItem{Reduced human intervention by \textbf{95\%} for key swaps by overhauling modem UI with \textbf{TypeScript React} to automate manual commands. }
      \resumeItem{Enhanced modem/network security by updating interfaces and \textbf{Docker} containers to utilize new SSL certificates from key swap tool. }
      \resumeItem{Boosted code coverage from \textbf{0\% to 90\%} by introducing \textbf{Jest} as the unit-testing framework, automating \textbf{100+} unit and end-to-end tests to mock user flow and backend responses. }
      \resumeItem{Seamlessly integrated multiple testing frameworks from \textbf{Go} and \textbf{JavaScript} into a single \textbf{CI/CD} pipeline via \textbf{Jenkins}. }
    \resumeItemListEnd

    % \altSubheading
    %   {UC San Diego CSE Department}{Undergraduate Researcher/Developer}{Feb. 2023 -- June 2024}
    %   \resumeItemListStart
    %     \resumeItem{Fine-tuned \textbf{computer vision machine learning} (ML) models such as Single-Shot-Detectors and YOLOv8 via \textbf{transfer learning} for localizing avacado nodes to identify effects of climate change on agriculture. }
    %     \resumeItem{\textbf{Mentored} younger members of AI lab by teaching ML models/concepts and delivering intuitive presentations of ML research papers. }
    %     \resumeItem{Addressed product-breaking bugs in state machine visualization and simulation tools used by \textbf{1000+} students per year.}
    % \resumeItemListEnd

% -----------Multiple Positions Heading-----------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 - Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd
  %  \resumeSubHeadingListEnd
%-------------------------------------------
    \altSubheading
    {UC San Diego CSE Department}{Undergraduate Tutor}{Sept. 2022 -- June 2024}
      \resumeItemListStart
        % \resumeItem{Guided \textbf{1500+} students in mastering Python, C, and ARM Assembly programming, and tools such as Git, and Bash. }
        % \resumeItem{Instructed \textbf{advanced algorithms}, \textbf{operating systems}, classical artificial intelligence, \textbf{machine learning} theory and implementation with optimization mathematics, scikit-learn, and \textbf{PyTorch}. }
        \resumeItem{Instructed \textbf{1500+} students in \textbf{machine learning} theory/implementation, scikit-learn, and \textbf{PyTorch}, \textbf{advanced algorithms}, \textbf{operating systems}, and classical \textbf{artificial intelligence}. }
        \resumeItem{Achieved \textbf{100\% student approval} across multiple courses by hosting office hours, and leading discussion sections to assist students with Python, C, ARM Assembly, and conceptual problems.}
        \resumeItem{Identified/patched \textbf{security vulnerabilities} for programming assignment autograders, eliminating most student autograder exploits.}
      \resumeItemListEnd

    \altSubheading
      {California Coast Credit Union}{Data Analytics Intern}{June 2022 -- August 2022}
      \resumeItemListStart
        \resumeItem{Developed and deployed an executive dashboard for viewing company-wide metrics related to call volume, call types, number of active users, number of transactions, etc. }
        \resumeItem{Wrote automated \textbf{SQL} scripts/queries for fetching/compiling data across multiple databases for dashboard.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
      {\href{}{\underline{\textbf{Steam Recommender}}} $|$ \emph{Pandas, NumPy, Scikit-Learn}}{}
      \resumeItemListStart
        % \resumeItem{Designed a collborative-filtering based \textbf{recommender system} to predict which games Steam users are likely to play. }
        \resumeItem{Ranked among the \textbf{top 0.3\%} participants in \textbf{machine learning competition} in both regression and classification tasks.}
        \resumeItem{Optimized models by \textbf{hyperparameter tuning} with grid search, cross-validation, and ensembling predictions. }
        \resumeItem{Utilized \textbf{natural language processing} techniques such as topic modeling to mitigate the cold-start problem.}
      \resumeItemListEnd
      \resumeProjectHeading
        {\href{https://github.com/ucsd-cse125-sp24/group5}{\underline{\textbf{Four Seasons}}} $|$ \emph{C++, OpenGL, GLSL}}{}
        \resumeItemListStart
          \resumeItem{ Four Seasons is a real-time, character-based, multiplayer 3D capture-the-flag shooter game, heavily inspired by classical music. }
          \resumeItem{ Designed and implemented a \textbf{custom graphics engine}, with support for textures, 3D animations, shadow mapping, non-photorealistic rendering, dynamic lighting/environments, and particles via instanced rendering. }
          \resumeItem{ Supported cross-platform development and gameplay by building custom operating system and architecture agnostic networking and graphics libraries. }
          \resumeItemListEnd
      % \resumeProjectHeading
      %     {\href{https://github.com/benjxia/notebookpicker}{\underline{\textbf{Notebook Picker}}} $|$ \emph{React, HTML, CSS, JavaScript, ASP.NET, C\#, Oracle Cloud}}{}
      %     \resumeItemListStart
      %       \resumeItem{Led team of 5 students to develop a full-stack web application for filtering laptops by specifications/price to assist with shopping.}
      %       \resumeItem{Planned and built a \textbf{REST API} for finding and filtering laptops based on CPU/GPU model, brands, release, etc. by querying from \textbf{Oracle Cloud} database with an ASP.NET backend.}
      %       \resumeItem{Reduced API response times by over \textbf{90\%} by caching SQL queries with Entity Framework Core object relational mapping.}
      %       \resumeItem{Designed wireframe layout in \textbf{Miro} and implemented routing and user interface with React.}
      %     \resumeItemListEnd
    \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}